Improved Bayesian Ethnorace Prediction

### 2021-02-14 paper.Rmd
real first draft yay

```{=tex}
\begin{singlespace}
Quantitative social science research on race and ethnicity can be constrained by the lack of available individual-level data with these markers. In response to this issue, methods have been developed to predict individuals' race and ethnicity using Bayes' rule. Racial distributions from the US Census Surname List are combined with distributions from geolocations, such as Census blocks or zip codes, to yield predicted probabilities of individuals' race and ethnicity. I expand upon existing methods by incorporating information from a nationwide list of first names as well as from residence characteristics. Along with some other adjustments, these improvements lead to substantial gains in predictive performance when validated against official state voter files. The largest of these predictive gains are found for African Americans and Hispanics---groups which existing methods find difficult to predict accurately without fine-grain geolocation information.
\end{singlespace}
```
# Introduction

Research on racial and ethnic disparities in the United States can be constrained by the lack of available individual-level data with these markers [@cascio2012; @kuk2020]. This is particularly true when racial geography is a key aspect of the research design. In these contexts, researchers are often forced to use aggregate-level data on group proportions, such as county statistics, to draw inferences. But this method is susceptible to the modifiable areal unit problem, whereby statistical bias is introduced due to arbitrary and unequal geographic unit sizes [@fotheringham1991]. Furthermore, some research designs all but require individual-level data. Geographic regression discontinuity designs---an increasingly common causal inference technique---typically relies on individually geocoded addresses [@keele2018; @velez2019; @cantoni2020]. Therefore if race or ethnicity are central elements of the research question, individual-level identifiers for these categories are likely necessary.

To overcome some of these challenges, in this paper I describe a method for imputing individual ethnorace categories directly. This method uses Bayes' rule to make predictions by combining information from nationwide distributions of six ethnoracial categories over other characteristics, such as names, geographies, political party identification, among others. My implementation builds off existing methods which use a similar prediction algorithm [@elliott2009; @imai2016; @voicu2018]. The method described in Imai and Khanna (2016) in particular, and the associated `R` package `wru`, has become popular in recent studies on race and ethnicity. Its application has been used in work on racial protests and voting patterns [@enos2019], disparities in campaign financing [@grumbach2020; @grumbach2020a], and public health issues such as suicide rates [@studdert2020].

My ethnorace prediction method improves upon Imai and Khanna (2016) in several ways. Whereas their method only takes as inputs distributions over surnames, geolocation, political party, age, and gender, my version adds information from a nationwide list of first names [@tzioumis2018] as well as address characteristics. Additionally, I incorporate insights from the machine learning literature to further improve predictive performance. The result of these modifications is a substantial increase in predictive power compared to Imai and Khanna (2016) in validation tests. These predictive gains are particularly strong in regards to correctly classifying African American and Hispanic individuals---especially in contexts where fine-grain geolocation data are unavailable. My method is available in an easy-to-use `R` package `bper`.[^1]

@@

In the next section I will provide some background on the inputs and outputs of my prediction method. Then I will explain the methodology and compare my implementation with previous versions. Finally, I will demonstrate the predictive performance of my method when validated against the combined North Carolina and Florida voter file ($n$ = 21,000,000).

@@

Before discussing the methodology further, I want to first define what "predicting ethnicity or race" means. These are categories which, although relatively immutable compared to other identities, do not have universally accepted delineations and meanings [@omi2014]. I follow the convention from previous ethnorace prediction methods by using the US Census Bureau categorizations [@elliott2009; @imai2016; @voicu2018]. In this framework, individuals can be classified as non-Hispanic White, non-Hispanic Black or African American, non-Hispanic Asian and Pacific Islander, non-Hispanic American Indian and Alaska Native, Hispanic or Latino alone, and non-Hispanic Other Race.[^2] Because Hispanic identity is defined by the Census, and understood commonly, as an ethnicity, rather than a race, I use the term "ethnorace" in this paper to refer to any of the previously-mentioned categories.

@@

There are a few benefits to using the Census ethnoracial categorization. This set captures a common understanding of race and ethnicity in the US, and correspond to the groups studied most frequently in social science research. The data sources of these groups' distributions that serve as inputs to the prediction formula also rely on the Census categorization. This also facilitates comparison of my method against previous ethnorace prediction methods.[^3] One downside to using the Census categories, however, is that it obscures substantial heterogeneity that may exist within each group. Within Asian Americans and Latinos, for example, there is considerable variation in terms of national ancestry. Furthermore, the unfortunate necessity of an Other Race category ensures that important sources of diversity are washed over.[^4]

@@

The first names list I use comes from Tzioumis (2017). It is drawn from mortgage applicants and contains ethnorace counts in each of the six categories across 4,250 first names. Unlike Census data, which form the basis for much of my other data sources, this list of first names may be unrepresentative of the larger US population. To the extent that first name distributions differ by ethnorace given employment status, for example, this may be a concern. But the predictive benefits from using first name data, as I will demonstrate, likely overwhelm these worries in most contexts.

@@

My ethnorace distributions by geographies come from the 2010 decennial Census, accessed via IPUMS NHGIS.[^6] In descending order of mean population, these geographies include *state*, *county*, *Census place*, *ZIP code*, and *Census block*. Predictions tend to improve with more precise levels of geography. With this in mind, my implementation automatically matches each individual to the most fine-grain level of geography available. As an aside, it is worth pointing out that this phenomenon is, in part, the consequence of generations of segregationist housing policies in the US. The fact that knowing an individual's ZIP code or Census block gives us so much knowledge about their race is an indictment of the US system more generally.

@@

The raw data sources I describe above, with the exception of party ID,[^8] all contain counts of individuals with a particular attribute (i.e. the first name JOHN, or the ZIP Code "92092") per ethnorace category. Taking proportions by cell across a particular attribute gives me $Pr(Ethnorace|Attribute)$, and taking proportions by cell across a particular ethnorace variable gives me $Pr(Attribute|Ethnorace)$. These two conditional probabilities form the building blocks of the classification algorithm described below.

@@

If any cell in the input data is empty (i.e. if there are no individuals of a particular ethnorace with some attribute), then the conditional probabilities $Pr(Ethnorace|Attribute)$ and $Pr(Attribute|Ethnorace)$ will be zero. As will become clear in the Methodology section, if either of those two probabilities for an individual equal zero for a given ethnorace, the algorithm will predict a zero percent probability that the individual belongs to that ethnorace. This will occur even if some other attributes about that individual predict a high probability of belonging to the ethnorace. For example, an individual could have first and last names that are highly predictive of being Hispanic, but reside in a Census block which had zero Hispanic occupants at the time of the 2010 decennial Census. Blocks typically contain only around 400 individuals---so this is a real possibility. For this person the input data says $Pr(Hispanic|Census Block) = 0$, which yields $Pr(Hispanic)= 0$ due to the structure of the formula. To resolve this issue, I apply a concept from the machine learning literature known as Laplace smoothing to my input data. This works by adding one to the count of individuals in every cell in the input data,[^9] and then calculating the conditional probabilities $Pr(Ethnorace|Attribute)$ and $Pr(Attribute|Ethnorace)$. I conjecture that absent this smoothing technique, the algorithm's predictions are too beholden to the specifics of the 2010 decennial Census. The predictions will generalize better to other time periods without the rigid assumptions of zero conditional probability for some attribute/ethnorace combinations.

@@

Where $x$ is the vector of individual attributes indexed by $j$. The particular attribute $x'$ comes from using the chain rule to decompose the joint probability $Pr(R=r, X)$. The choice of which attribute to use for $x'$ is atheoretical, but all previous prediction methods have used last names [@elliott2009; @imai2016; @voicu2018]. During my validation exercises, I found that the choice of $x'$ has potentially large consequences for predictive performance. For example, using last names for $x'$ appears to help predictions of Whites---but to the detriment of non-Whites. In light of these trade-offs, my method cycles through every attribute as the choice of $x'$ and computes $Pr(R=r|X)$ for each. These posterior probabilities are then averaged within each ethnoracial category to generate final predicted probabilities that an individual belongs to a particular ethnorace. The end result is more balanced predictions across each ethnorace.

@@

Violations of the conditional independence assumption are commonplace in most applications of similar classification algorithms. Nevertheless, these prediction methods perform unreasonably well in many contexts [@lewis1998; @domingos1997; @rish2001]. This is likely because of the decision rule governing the final classifications---the posterior probabilities the true class do not have to necessarily be statistically valid, they only need to be higher than those of every other class to be accurately classified. For this reason, as more attribute inputs are added to the model (first names, multi-unit occupancy), I believe researchers should be cautious when trying to interpret the values of $Pr(R=r|X)$ directly. Rather, the maximum a posteriori ethnorace classifications should be used alone

@@

To perform the validation tests, I first geocoded each unique address in the North Carolina/Florida voter file. This allowed me to match individual observations to Census places and blocks, and ZIP codes. Then I applied the prediction algorithm described above using the `bper` package and calculated each individuals' predicted ethnorace. In order to compare my method against an existing benchmark, I also used the `wru` package [@imai2016] to calculate ethnorace predictions for the same individuals.[^10]

[^10]: Unless otherwise noted, each prediction method is using the full set of available attributes for its predictions.

@@

Figure 1 displays how well each prediction method recovers the true ethnorace proportions in the North Carolina/Florida voter file. For each group, my method using the `bper` package estimates smaller differences in proportions (i.e. closer to horizontal line at zero in the figure). In the case of African Americans this difference is cut in half. Both prediction methods share a pattern in overestimating certain group and underestimating others. While it is reassuring to be able to recover close to the true population proportions for each group, this is a poor metric for assessing predictive performance. Most researchers probably care more about individual-level predictions rather than population-level predictions.

The most straightforward metric for assessing individual-level predictive performance is the Accuracy score, or Overall Error Rate. This number is the proportion of correctly classified individuals in the sample. I ran the model separately for different combinations of input variables to mimic data availability constraints in real-world applications, and then calculated the Accuracy score for each. Figure 2 displays a summary of the results of these different models.

@@

As expected, the model with the greatest number of input data sources, and at the most precise geographic level, on the far left of the figure performs the best in terms of overall Accuracy. Using Census blocks, multi-unit address, party ID, first names, and last names, this model correctly identifies the ethnorace of `r round(subset(tests, select = "accuracy", test_method == "bper" & test_type == "all"), 3) * 100`% of individuals in the sample. The downward trend in model accuracy seen in the figure corresponds to expanding the size of the geolocation variable. Moving from blocks to ZIP codes, to places, to counties, and to states all decrease the overall predictive performance. I include the input for multi-unit occupancy only for the Census block models because I believe this reflects the practical contexts where `bper` might be used. If a researcher has access to individual-level addresses, they should be able to geocode these to find the matching Census blocks and should also be able to parse the unit type. But researchers relying on more aggregate geographies likely do not have access to individual addresses, and hence the unit types, for their sample.[^11] In Figure 2 I also pair each geolocation variable with a model missing the party ID input. The losses to predictive performance across all geographies appears roughly uniform with the removal of party ID.

[^11]: In the event that data is available, adding multi-unit occupancy inputs to aggregate geographies, such as ZIP codes, places, counties, or states *greatly* enhances the predictive accuracy of the model.

@@

@@

Precision/Recall. Precision is the percentage of correctly classified individuals among all individuals predicted to belong to a specific ethnorace. It answers the question of how likely an individual's predicted ethnorace in our sample matches their true ethnorace. Recall, also known as Sensitivity or the True Positive Rate, is the percentage of all individuals who belong to a specific ethnorace which the model correctly classifies.

I believe these are the two best metrics with which to evaluate the predictive performance of the algorithm. Precision and Recall reflect substantively important concerns for its real-world applications, and the inherent trade-offs between optimizing for either metric provides a balanced assessment of the results. On the one hand, Precision rewards very conservative classification procedures. We could, for example, only classify individuals as White if their posterior probability of being White was greater than 99%. This would ensure a very high Precision score for Whites because we are only capturing the low-hanging fruit. A conservative classification procedure like this, however, would likely result in extremely low Recall for Whites. If we only capture the low-hanging fruit, a greater share of White individuals will be mis-classified. Likewise, optimizing the algorithm for perfect Recall for Whites is trivial. By classifying every individual as White, we ensure 100% of Whites are correctly classified. Of course this procedure would result in extremely low Precision for Whites because so many non-Whites would be classified as White. Achieving both high Precision and high Recall, therefore, is a difficult task.

Figure 3 displays the Precision and Recall scores broken down by ethnorace for the same models used in Figure 2.[^12] For both Whites and Hispanics, Precision and Recall remain high across all models. Using the most input data available (the models on the far left of the figure), White Precision and Recall are `r round(subset(tests, select = "prec_white", test_method == "bper" & test_type == "all"), 3)` and `r round(subset(tests, select = "rec_white", test_method == "bper" & test_type == "all"), 3)`, respectively. And Hispanic Precision and Recall are `r round(subset(tests, select = "prec_hispanic", test_method == "bper" & test_type == "all"), 3)` and `r round(subset(tests, select = "rec_hispanic", test_method == "bper" & test_type == "all"), 3)`, respectively. These metrics are uniformly lower for Asians---likely reflecting the relative rarity of Asian individuals in the sample. When using Census blocks as the unit of geography, predictions for African Americans are strong (Precision: `r round(subset(tests, select = "prec_black", test_method == "bper" & test_type == "all"), 3)`, Recall: `r round(subset(tests, select = "rec_black", test_method == "bper" & test_type == "all"), 3)`). But predictive performance falls steeply with broader geolocations. At the state level, without party ID, Black Precision is `r round(subset(tests, select = "prec_black", test_method == "bper" & test_type == "state_np"), 3)` and Recall is `r round(subset(tests, select = "rec_black", test_method == "bper" & test_type == "state_np"), 3)`. This difference in predictive performance between geographies suggests patterns of racial segregation in at least the North Carolina and Florida sample.

[^12]: The model names are abbreviated by the level of geography, and all use first name and last name inputs. Models with *(np)* do not use the party ID inputs.

[*insert paragraph summing up results*]

@@

The classification metrics detailed above provide some information about the predictive shortcomings of my method. These limitations notwithstanding, however, the ethnorace predictions made by `bper` are nearly uniformly better than those from `wru`. Figure 4 displays the difference in Accuracy between `bper` and `wru` using the same input data discussed previously.[^13] The baseline of zero in the figure represents the Accuracy scores from each model using `wru`, and the height of the bars display the change in Accuracy using `bper`. Across all model types, `bper` scores between 1.5 and 3.5 percentage points higher on this metric. Regardless of input data, `bper` classifies a higher proportion of individuals correctly in the North Carolina/Florida voter file.

[^13]: The `wru` package does not provide ZIP code or state level predictions so those models are excluded from the comparison.

Figures 5 through 8 show the same comparisons between `wru` and `bper` for Precision and Recall across different ethnoraces. For Asians in Figure 5, the comparisons shows absolute gains for `bper` in both metrics for most model types. When using place-level geography, and county-level without party ID, there is some loss to Recall. But the large gains in Precision should outweigh these concerns. The comparison among predictions for Black individuals in Figure 6 are striking. Despite slightly lower Recall scores across all model types, my method shows dramatic gains in Precision at the broader geographic levels. Without party ID, `bper` improves upon `wru` by at least 30 percentage points in Precision using place or county geolocations. Figure 7 shows the comparison in predictions among Hispanics. Here `bper` out-performs `wru` in both Precision and Recall for every model. The magnitudes of these differences, however, are more modest than those for Black or Asian predictions. This is likely due to distinct Spanish last names, which already provide a lot of predictive information for Hispanics. Lastly, Figure 8 displays the more mixed results for the White predictions. When using all available input data for both methods (the left-most model), `bper` out-performs `wru` on both Precision and Recall for White individuals. In every other model, however, losses to Precision are compensated with gains in Recall. This means that, while `bper` is doing a better job classifying a higher proportion of Whites, it is mis-classifying more non-Whites as White compared to `wru`.

>>>>

```{=tex}
\begin{singlespace}
Quantitative social science research on race and ethnicity can be constrained by the lack of available individual-level data with these markers. In response to this issue, methods have been developed to predict individuals' race and ethnicity using Bayes' rule. Racial distributions from the US Census Surname List are combined with distributions from geolocations, such as Census blocks or zip codes, to yield predicted probabilities of individuals' race and ethnicity. I expand upon existing methods by incorporating information from a nationwide list of first names as well as from residence characteristics. Along with some other adjustments, these improvements lead to substantial gains in predictive performance when validated against official state voter files. The largest of these predictive gains are found for African Americans---a group which existing methods find difficult to predict accurately.
\end{singlespace}
```
# Introduction

Research on racial and ethnic disparities in the United States can be constrained by the lack of available individual-level data with these markers [@cascio2012; @kuk2020]. This is particularly true when racial geography is a key aspect of the research design. In these contexts, researchers are often forced to use aggregate-level data on group proportions, such as county statistics, to draw inferences. But this method is susceptible to the modifiable areal unit problem, whereby statistical bias is introduced due to arbitrary and unequal geographic unit sizes [@fotheringham1991]. Furthermore, some research designs all but require individual-level data. Geographic regression discontinuity---an increasingly common causal inference technique---typically relies on individually geocoded addresses [@keele2018; @velez2019; @cantoni2020]. Therefore if race or ethnicity are central elements of the research question, individual-level identifiers for these categories are likely necessary.

To overcome some of these challenges, I describe a method for imputing individual ethnoraces directly. This method uses Bayes' rule to make predictions by combining information from nationwide distributions of six ethnorace categories over other characteristics, such as names, geographies, political party identification, and others. My implementation builds off existing methods which use a similar prediction algorithm [@elliott2009; @imai2016; @voicu2018]. The method described by Imai and Khanna (2016) in particular, and the associated `R` package `wru`, has become popular in recent studies on race and ethnicity. Its application has been used in work on racial protests and voting patterns [@enos2019], disparities in campaign financing [@grumbach2020; @grumbach2020a], and public health issues such as suicide rates [@studdert2020].

My ethnorace prediction method improves upon Imai and Khanna (2016) version in several ways. Whereas their method only takes as inputs distributions over surnames, geolocation, political party, age, and gender, my implementation adds information from a nationwide list of first names [@tzioumis2018] as well as address characteristics. Additionally, I incorporate insights from the machine learning literature to further improve predictive performance. The result of these modifications is a substantial increase in predictive power compared to Imai and Khanna (2016) in validation tests. These predictive gains are particularly strong in regards to correctly classifying African American and Hispanic individuals---especially in contexts where fine-grain geolocation data are unavailable. My method is available in an easy-to-use `R` package `bper`.[^1]

@@

In the next section I provide some background and specifics regarding the inputs and outputs of my ethnorace prediction method. Then I explain the methodology and compare my implementation with previous versions. Finally, I demonstrate the predictive performance of my method when validated against the combined North Carolina and Florida voter file ($n$ = 21,164,503).

@@

Before discussing the methodology further, I want to first define what "predicting ethnicity or race" means. These are categories which, although relatively immutable compared to other identities, do not have universally accepted delineations and meanings [@omi2014]. I follow the convention from previous ethnorace prediction methods by using the US Census Bureau categorizations [@elliott2009; @imai2016; @voicu2018]. In this framework, individuals can be classified as non-Hispanic White, non-Hispanic Black or African American, non-Hispanic Asian and Pacific Islander, non-Hispanic American Indian and Alaska Native, Hispanic or Latino alone, and non-Hispanic Other Race.[^2] Because Hispanic identity is defined by the Census, and understood commonly, as an ethnicity, rather than a race, I use the term "ethnorace" in this paper to refer to any of the previously-mentioned groups.

@@

There are a few benefits to using the Census ethnorace categorization. These definitions capture a common understanding of race and ethnicity in the US, and correspond to the groups studied most frequently in social science research. The data sources of these groups' distributions that serve as inputs to the prediction formula also rely on the Census categorization. This also facilitates comparison of my method against previous ethnorace prediction methods.[^3] One downside to using the Census categories, however, is that it obscures substantial heterogeneity that may exist within each group. Within Asian Americans and Latinos, for example, there is considerable variation in terms of national ancestry. Furthermore, the unfortunate necessity of catch-all Other Race category ensures that important sources of diversity are washed over.[^4]

@@

The first names list I use comes from Tzioumis (2017). It is drawn from mortgage applications and contains ethnorace counts in each of the six groups across 4,250 first names. Unlike Census data, which form the basis for much of my other data sources, this list of first names may be unrepresentative of the larger US population. To the extent that first name distributions differ by ethnorace given employment status, for example, this may be a concern. But the predictive benefits from using first name data, as I will demonstrate, likely overwhelm these worries in most contexts.

@@

My ethnorace distributions by geographies come from the 2010 decennial Census, accessed via IPUMS NHGIS.[^6] In decreasing order of mean population, these geographies include *state*, *county*, *Census place*, *ZIP code*, and *Census block*. Predictions tend to improve with more precise levels of geography. With this in mind, my implementation automatically matches each individual to the most fine-grain level of geography available. As an aside, it is worth pointing out that this phenomenon is, in part, the consequence of generations of segregationist housing policies in the US. The fact that knowing an individual's ZIP code or Census block gives us so much knowledge about their race is an indictment of the US system more generally.

@@

The raw data sources I describe above, with the exception of party ID,[^8] all contain counts of individuals with a particular attribute (i.e. the first name JOHN, or the ZIP Code "92092") per ethnorace category. Taking proportions by cell across a given attribute tells us $Pr(Ethnorace|Attribute)$, and taking proportions by cell across a given ethnorace group tells us $Pr(Attribute|Ethnorace)$. These two conditional probabilities form the building blocks of the classification algorithm described late.

@@

If any cell in the input data is empty (i.e. if there are no individuals of a particular ethnorace with some attribute), then the conditional probabilities $Pr(Ethnorace|Attribute)$ and $Pr(Attribute|Ethnorace)$ will be zero. As will become clear in the Methodology section, if either of those two probabilities for an individual equal zero for a given ethnorace, the algorithm will predict a zero percent probability that the individual belongs to that ethnorace. This will occur even if some other attributes about that individual predict a high probability of belonging to the ethnorace. For example, an individual could have first and last names that are highly predictive of being Hispanic, but reside in a Census block which had zero Hispanic occupants at the time of the 2010 decennial Census. Blocks typically contain only around 400 individuals---so this is a real possibility. For this person the input data claims that $Pr(Hispanic|Census Block) = 0$, which yields $Pr(Hispanic)= 0$ due to the structure of the prediction algorithm. To resolve this issue, I apply a technique from the machine learning literature known as Laplace smoothing to my input data. This works by adding one to the count of individuals in every cell in the input data,[^9] then calculating the conditional probabilities $Pr(Ethnorace|Attribute)$ and $Pr(Attribute|Ethnorace)$. I conjecture that absent this smoothing technique, the algorithm's predictions are too beholden to the specifics of the 2010 decennial Census. The predictions will generalize better to other time periods without the rigid assumptions of zero conditional probability for some attribute/ethnorace combinations.

@@

Where $x$ is the vector of individual attributes indexed by $j$. The particular attribute $x'$ comes from using the chain rule to decompose the joint probability $Pr(R=r, X)$. The choice of which attribute to use for $x'$ is atheoretical, but all previous prediction methods have used last names [@elliott2009; @imai2016; @voicu2018]. During my validation exercises, I found that the choice of $x'$ has potentially large consequences for predictive performance. For example, using last names for $x'$ appears to help predictions of Whites---but to the detriment of non-Whites. In light of these trade-offs, my method cycles through every attribute as the choice of $x'$ and computes $Pr(R=r|X)$ for each. These posterior probabilities are then averaged within each ethnoracial category to generate final predicted probabilities that an individual belongs to a particular ethnorace. The result is more balanced predictions across each ethnorace.

@@

Violations of the conditional independence assumption are commonplace in most applications of similar classification algorithms. Nevertheless, these prediction methods perform unreasonably well in many contexts [@lewis1998; @domingos1997; @rish2001]. This is likely because of the decision rule governing the final classifications---the posterior probabilities of the true class do not have to necessarily be statistically valid, they only need to be higher than those of every other class to be accurately classified. For this reason, as more attribute inputs are added to the model (first names, multi-unit occupancy) researchers should be cautious trying to interpret the posterior probabilities $Pr(R=r|X)$ directly. Rather, the maximum a posteriori ethnorace classifications should be used alone.

@@

After combining the two voter files, I then geocoded each unique address in the sample. This allowed me to match individual observations to Census places and blocks, and ZIP codes. Then I applied the prediction algorithm described above using the `bper` package and calculated each individuals' predicted ethnorace. In order to compare my method against an existing benchmark, I also used the `wru` package [@imai2016] to calculate ethnorace predictions for the same individuals.

@@

Figure 1 displays how well each prediction method recovers the true ethnorace proportions in the North Carolina/Florida voter file. For each group, my method using the `bper` package estimates smaller differences in proportions (i.e. closer to horizontal line at zero in the figure). In the case of African Americans this difference is cut in half. Both prediction methods share a pattern in overestimating certain group and underestimating others. While it is reassuring to be able to recover close to the true population proportions for each group, this is not a fully satisfactory test for assessing predictive performance. Individual-level performance is more substantively important than aggregate predictions.

The most straightforward metric for assessing individual-level predictive performance is the Accuracy score, or Overall Error Rate. This number is the proportion of correctly classified individuals in the sample. I ran models separately for different combinations of input variables to mimic data availability constraints in real-world applications, and then calculated the Accuracy score for each. Figure 2 displays a summary of the results of these different models.

@@

As expected, the model with the greatest number of input data sources, and at the most precise geographic level, on the far left of the figure performs the best in terms of overall Accuracy. Using Census blocks, multi-unit address, party ID, first names, and last names, this model correctly identifies the ethnorace of `r round(subset(tests, select = "accuracy", test_method == "bper" & test_type == "all"), 3) * 100`% of individuals in the sample. The downward trend in model accuracy seen in the figure corresponds to expanding the size of the geolocation variable used. Moving from blocks to ZIP codes, then to places, then to counties, and finally to states all decrease the overall predictive performance in terms of overall Accuracy. I include the input for multi-unit occupancy only for the Census block models because I believe this reflects the practical contexts where `bper` might be used. If a researcher has access to individual-level addresses, they should be able to geocode these to find the matching Census blocks and should also be able to parse the residency type (multi-unit or stand-alone). But researchers relying on more aggregate geographies likely do not have access to individual addresses, and hence the residency characteristics, for their sample.[^10] In Figure 2 I pair each geolocation variable with a model missing the party ID input. The losses to predictive performance across all geographies appears roughly uniform with the removal of party ID.

[^10]: In the event that data is available, adding multi-unit occupancy inputs to aggregate geographies, such as ZIP codes, places, counties, or states *greatly* enhances the predictive accuracy of the model.

@@

I believe the two best metrics to assess group-level predictions are Precision and Recall. Precision is the percentage of correctly classified individuals among all individuals predicted to belong to a specific ethnorace. It answers the question of how likely an individual's predicted ethnorace in our sample matches their true ethnorace. Recall, also known as Sensitivity or the True Positive Rate, is the percentage of all individuals who belong to a given ethnorace group which the model correctly classifies.

Precision and Recall reflect substantively important concerns for real-world applications of the method, and the inherent trade-offs between optimizing for either metric provide a balanced assessment of the predictive performance. On the one hand, Precision rewards very conservative classification procedures. We could, for example, only classify individuals as White if their posterior probability of being White was greater than 99%. This would ensure a very high Precision score for Whites because we are only capturing the low-hanging fruit. A conservative classification procedure like this, however, would likely result in extremely low Recall for Whites. If we only capture the low-hanging fruit, a greater share of White individuals will be mis-classified. Likewise, optimizing the algorithm for perfect Recall for Whites is trivial. By classifying every individual as White, we ensure 100% of Whites are correctly classified. Of course this procedure would result in extremely low Precision for Whites because so many non-Whites would be classified as White as well. Achieving both high Precision and high Recall, therefore, is a difficult task.

@@

Figure 3 displays the Precision and Recall scores broken down by ethnorace for the same models used in Figure 2.[^11] For both Whites and Hispanics, Precision and Recall remain high across all models. Using the most input data available (the models on the far left of the figure), White Precision and Recall are `r round(subset(tests, select = "prec_white", test_method == "bper" & test_type == "all"), 3)` and `r round(subset(tests, select = "rec_white", test_method == "bper" & test_type == "all"), 3)`, respectively. Hispanic Precision and Recall in this model are `r round(subset(tests, select = "prec_hispanic", test_method == "bper" & test_type == "all"), 3)` and `r round(subset(tests, select = "rec_hispanic", test_method == "bper" & test_type == "all"), 3)`, respectively. These metrics are uniformly lower for Asians---likely reflecting the relative rarity of Asian individuals in the sample. When using Census blocks as the unit of geography, predictions for African Americans are strong (Precision: `r round(subset(tests, select = "prec_black", test_method == "bper" & test_type == "all"), 3)`, Recall: `r round(subset(tests, select = "rec_black", test_method == "bper" & test_type == "all"), 3)`). But predictive performance falls with broader geolocations. At the state level, without party ID, Black Precision is `r round(subset(tests, select = "prec_black", test_method == "bper" & test_type == "state_np"), 3)` and Recall is `r round(subset(tests, select = "rec_black", test_method == "bper" & test_type == "state_np"), 3)`. This difference in predictive performance between geographies suggests patterns of racial segregation in at least the North Carolina and Florida sample.

[^11]: The model names are abbreviated by the level of geography, and all use first name and last name inputs. Models with *(np)* do not use the party ID inputs.

[*insert paragraph or few sentences summing up results*]

@@

The classification metrics detailed above provide some information about the predictive shortcomings of my method. These limitations notwithstanding, however, the ethnorace predictions made by `bper` are nearly uniformly better than those from `wru`. Figure 4 displays the difference in Accuracy between `bper` and `wru` using the same input data discussed previously.[^12] The baseline of zero in the figure represents the Accuracy scores from each model using `wru`, and the height of the bars display the change in Accuracy using `bper`. Across all model types, `bper` scores between 1.5 and 3.5 percentage points higher on this metric. Regardless of input data, `bper` classifies a higher proportion of individuals correctly in the North Carolina/Florida voter file.

[^12]: The `wru` package does not provide ZIP code or state level predictions so those models are excluded from the comparison.

Figures 5 through 8 show the same comparisons between `wru` and `bper` for Precision and Recall across different ethnoraces. For Asians in Figure 5, the comparisons shows absolute gains for `bper` in both metrics for most model types. When using place-level geography, and county-level without party ID, there is some loss to Recall. But the large gains in Precision for Asians should outweigh these concerns. The comparison among predictions for Black individuals in Figure 6 are striking. Despite slightly lower Recall scores across all model types, my method shows dramatic gains in Precision at the broader geographic levels. Without party ID, `bper` improves upon `wru` by at least 30 percentage points in Precision using place or county geolocations.

Figure 7 shows the comparison in predictions among Hispanics. Here `bper` out-performs `wru` in both Precision and Recall for every model. The magnitudes of these differences, however, are more modest than those for Black or Asian predictions. This is likely due to distinct Spanish last names, which already provide a lot of predictive information for Hispanics. Lastly, Figure 8 displays the more mixed results for the White predictions. When using all available input data for both methods (the left-most model), `bper` out-performs `wru` on both Precision and Recall for White individuals. In every other model, however, losses to Precision are compensated with gains in Recall. This means that, while `bper` is doing a better job classifying a higher proportion of Whites, it is mis-classifying more non-Whites as White compared to `wru`.
